method

### 2021-12-02 06_Paper/ER-ED/method.Rmd
added ANOVA for subjective arousal

library(targets) # to keep track of all relevant files
library(readxl) # import excel files
library(here) # to set directories without defined paths
library(papaja) # APA conform output

@@

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots

@@

```{r statistics, echo=FALSE, message=FALSE, warning=FALSE}

# ANOVA subjective arousal ratings

aov.arousal = afex::aov_ez(id = "ID",    #ATTENTION: needs pagacke "afex"
                      dv = "arousal",
                      data = data_ER,
                      within = "block",
                      fun_aggregate = mean) 
afex::nice(aov.arousal, es = "pes")

# compute posthoc tests for both within measures
posthoc_test_strategy = emmeans::emmeans(aov.arousal$aov, specs = "block")
pairs(posthoc_test_strategy, adjust = "bonferroni")
```
